Resource Buying Games

### 2017-04-07 paper.tex
sent version

We start by defining an appropiate congestion model and an associated
strategic game as well as by introducing matroids as combinatorial structures
to model desired configurations of resources for players. Following we present
an algorithm to compute PNEs in unweighted matroid games with marginally
non-increasing cost functions and its correctness proof.
Afterwards, we examine weighted matroid games with different cost functions
and concludingly, we study non-matroid configuration spaces.

@@

iteratively adding one element from a cut and contracting the matroid to the
added element while deleting all other elements from the cut. Since cuts are
inclusion-wise minimal deleting all but one element from one cut leaves at
least one possible basis for the player available. For every player we maintain
the elements which are chosen for her/him up to the current state

@@

the correctness of the algorithm. Because, if we assume to have a beneficial
alternative to the computed basis for one player there must exist an element

@@

  are not ordered by $\subseteq$) on a set of resources $E$, there exists a
  weighted two-player resource buying game $G = \tupel{\tilde{E},

>>>>

We start by defining an appropiate congestion model and an associated
strategic game as well as by introducing matroids as combinatorial structures
to model desired configurations of resources for players. Following, we present
an algorithm to compute PNEs in unweighted matroid games with marginally
non-increasing cost functions and its correctness proof.
Afterwards, we examine weighted matroid games with different cost functions
and concludingly, we study non-matroid configuration spaces.

@@

iteratively adding one element from a cut and contracting the matroid of the
player to the added element while deleting all other elements from the cut.
Since cuts are inclusion-wise minimal deleting all but one element from one cut
leaves at least one possible basis for the player available. For every player
we maintain the elements which are chosen for her/him up to the current state

@@

the correctness of the algorithm because, if we assume to have a beneficial
alternative to the computed basis for one player, there must exist an element

@@

  are pairwisely not ordered by $\subseteq$) on a set of resources $E$, there
  exists a weighted two-player resource buying game $G = \tupel{\tilde{E},
